Data Preparation

### 2019-01-10 Data Preparation.Rmd
Text in Textual Data

##Textual Data
### Course Catalogue
In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.

#### Extracting Overviews
We start by extracting the overviews which are 1 or 2 page long and contain important information of a course. To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`). These pages are typically headers. Excluding them before the analysis allows use to keep the code relatively simple. We also make use the fact that the overviews always start with the code of the course, i.e. it starts with one of the elements of `course_code` and use `grep` to identify the first page of each overview. We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.

>>>>

##Textual Data
### Course Catalogue
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.

#### Extracting Overviews

We start by extracting the overviews which are 1 or 2 page long and contain important information of a course. To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`). These pages are typically headers. Excluding them before the analysis allows use to keep the code relatively simple. We also make use the fact that the overviews always start with the code of the course, i.e. it starts with one of the elements of `course_code`; and we use `grep` to identify the first page of each overview. We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.
